### 2010-04-05 resume_cv/cv.tex
Added a "graduated" line to my cv
Added a link to the blog post for my Google intern project
Fixed a small typo in my cv
Updated my CV to include the poster presentation I did

\section{Research Interests}
%
Particle swarm optimization, natural language processing, Bayesian machine
learning, Markov decision processes, value iteration

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] B.S.,
		Computer Science, April 2010
        \begin{innerlist}
        \item Minors in Physics and Mathematics
        \item Thesis Topic: \emph{Speculative Evaluation in Particle Swarm
            Optimization}
        \item Adviser: Professor Kevin Seppi
        \end{innerlist}

@@

    \item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  Submitted to: \emph{The
	  Genetic and Evolutionary Computation Conference, 2010}.  Awaiting
	  acceptance notification.
\end{bibsection}

@@

\item[] \textit{Software Engineering Intern for the TV Ads Team}%
        \hfill \textbf{May 2009 to August 2009}
\begin{innerlist}
\item Used machine learning techniques to attribute calls received by
  advertisers to specific ads played on TV networks.
\item Gave several presentations to the machine learning lunch group.
\end{innerlist}

>>>>

\section{Research Interests}
%
Particle swarm optimization, natural language processing, Latent Dirichlet
Allocation, Bayesian machine learning, Markov decision processes, value
iteration

\section{Education}
%
{\textbf{Brigham Young University}},
Provo, Utah USA
\begin{outerlist}
\item[] B.S.,
		Computer Science, April 2010
        \begin{innerlist}
        \item Minors in Physics and Mathematics
        \item Graduated with a 4.0 GPA and University honors (anticipated)
        \item Thesis Topic: \emph{Speculative Evaluation in Particle Swarm
            Optimization}
        \item Advisor: Professor Kevin Seppi
        \end{innerlist}

@@

	\item Matthew Gardner and Eric Ringger.  Automatic Topic Discovery in 100
	  Years of General Conference Talks.  Presented at the 50th Anniversary
	  BYU Studies Symposium, 2010.

	\item Matthew Gardner, Andrew McNabb, and Kevin Seppi.  Speculative
	  Evaluation in Particle Swarm Optimization.  Submitted to:
	  \emph{Transactions on Evolutionary Computation}.  Awaiting acceptance
	  notification.
\end{bibsection}

@@

\item[] \textit{Software Engineering Intern for the TV Ads Team}%
        \hfill \textbf{May 2009 to August 2009}
\begin{innerlist}

\item Used machine learning techniques to attribute calls received by
  advertisers to specific ads played on TV networks.  Official blog post about
  my project can be found at:
  http://google-tmads.blogspot.com/2010/01/track-cost-per-call-data-through-google.html.
\item Gave several presentations to the machine learning lunch group.
\end{innerlist}
